Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-11-24 RR_manuscript/Draft_RR.Rmd
rr updates

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below). <!-- TR: Big to-do point. We need to only justify a minimum sample size-->
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels. 
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses. 
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses). 
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript. 
All analysts will sign a consent (ethics) document (LINK).

@@

## Step 3: Peer Reviews of Analyses 
<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->

@@

<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS-->

@@

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

>>>>

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below). <!-- TR: Big to-do point. We need to only justify a minimum sample size JC: added description (word for word) from ecology RR. Need to figure out what it means still and then put into our own words. -->
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels. 
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses. 
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses). 
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript. 
All analysts will sign a consent (ethics) document (LINK).

<!-- sample size info from Ecology RR -->
We identified our minimum number of analyses per data set by considering the number of effects needed in a meta-analysis to generate an estimate of heterogeneity ($\tau^2$) with a 95% confidence interval that does not encompass zero. 
This minimum sample size is invariant regardless of $\tau^2$. 
This is because the same t-statistic value will be obtained by the same sample size regardless of variance ($\tau^2$). 
We see this by first examining the formula for the standard error, SE for variance, ($\tau^2$) or SE($\tau^2$) assuming normality in an underlying distribution of effect sizes (Knight 2000):

$$SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}$$

and then rearranging the above formula to show how the t-statistic is independent of $\tau^2$, as seen below.

$$t = \frac{\tau^2}{SE(\tau^2)} = \sqrt{\frac{(n-1)}{2}}$$

We then find a minimum n = 12 according to this formula. 
<!-- We need to decide if we use this (I still don't understand it) -->

@@

## Step 3: Peer Reviews of Analyses

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->

@@

<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS ... ARE WE STILL DOING THIS? -->

<!-- description of meta-analysis starts here -->

Upon calculating a standardized effect size and standard error for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:

$$
\begin{aligned}
\delta_t & \sim \text{Normal}(\theta_i, \sigma_i = \text{se}_i) \\
\theta_i     & \sim \text{Normal} (\mu, \tau) \\
\mu          & \sim \text{Normal} (0, 1) \\
\tau         & \sim \text{HalfCauchy} (0, 1)
\end{aligned}
$$

Effect size ($\delta_{t}$) is the outcome variable and the number of post-hoc changes and the number of models fit will be included as population-level effects (i.e., fixed effects). 
The likelihood of the outcome variable is assumed to be normally distributed.
Analysis teams and reviewers will be included as group-level effects (i.e., random effects). 
For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1. 
A cauchy prior set at 0 with scale 1 will be used for $\tau$. 
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019).

<!-- Sorensen analysis starts here -->

The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other. 
Specifically, we will explain how team effect sizes deviate from the pooled estimate based on a measure of the uniqueness of the set of variables included in each analysis. 
We will use Sorensen's Similarity Index (SSI) to derive a 'uniqueness' score. 
The SSI is an index typically used in ecology research to compare species composition across sites. 
For our purposes, we will treat variables as species and individual analyses as sites.
In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al. 2018) in R. 
We achieve this using the following formula:

$$\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}$$

where, given a pair of models, a is the number of variables common to both, b is the number of variables that occur in the first model but not in the second, and c is the number of variables that occur in the second model but not in the first. 
We then will use the per-model average Sorensen's index value as an independent variable to predict the deviation score in a general linear model, with no random effect since each analysis is included only once, in the stats package in R  (R_Core_Team 2019):
<!-- are we going to do this last part? -->

@@

SAMPLE SIZE

META ANALYSIS

SOreenson analysis
